---
title: "Boar_Data_Markdown"
author: "shelleydan"
date: "2024-11-04"
output: html_document
---

```{r setup, include=FALSE}
workDir <- "~/mydata/BIT107-Boar-Markdown/"
projectName <- "Boar_Data_R_Markdown.R"
```

For the analysis of this data set (Boar.csv), there are a few specific packages that need to be installed first. 

```{r Packages, include=FALSE}
#Downloading Packages and Loading Libraries
#install.packages("dplyr")
#library(dplyr)
```

The first step is to read in the Boar data ("Boar.csv") which includes information based on their size (length) and TB status (tb). The goal of this analysis is to build a generalised linear model (GLM) to predict the possibility of a Boar being infected with TB based on their body length. 

```{r loading_data}
boar_data <- read.csv("Boar.csv", header = T, na = "NA", stringsAsFactors = T)

```

Firstly, we want to look at some basic data exploration before we make our model. Here we plot all variable against each other and look at the structure of the data frame. 

```{r data_exploration}
#pairs(boar_data)
#glimpse(boar_data)
```

Now that we understand our data format, we can start building our model. We identifiy the range of the data in length to apply to our model later. Finally we summarise our model afterwards to understand the statistical output. 

```{r model_generation, align='c'}
range(boar_data$length, na.rm = T) #Gives the range of the data input 

model1 <- glm(Tb~length, data = boar_data, na.action = na.omit, family=binomial(link = "logit"))
#We know to use binomial because the TB (y) only takes values of 0 or 1. 
#logit is a value of the log of odds. 

par(mfrow=c(2,2))
plot(model1) #Plots the 4 residual plot. 
#1: The top and bottom should not cross the middle line, this means that theres no false positive or false negative
par(mfrow=c(1,1))

summary(model1)
```

The final step is to build our prediction graphically. 

```{r Graphical_representation}
plot(Tb ~ length, data = boar_data)

newDat <- expand.grid(length = seq(46.5,165,0.5))

pred <- predict(model1, newdata = newDat, 
                type = "response", se.fit = T, na.rm = T)
#se.fit allows you to include the standard error within it
#This expand must include all X variables we include in our model. The seq(min, max, stepwise_change/intervals)
#Why do we have different types of 'type'?

predFrame <- data.frame(pred, length = newDat$length) #Combinging the datasets
head(predFrame)

plot(Tb ~ length, data = boar_data) #Empty plot of just Tb and Length

#Perfect Prediction line
lines(fit ~ length, data = predFrame, lw = 1.5, col = "blue") #Adds the middle line

#Predictions +/- the error. 
lines(fit+se.fit ~ length, data = predFrame, lw = 1.5, col = "blue", lty = 2)
lines(fit-se.fit ~ length, data = predFrame, lw = 1.5, col = "blue", lty = 2)

```

