---
title: "Boar_Data_Markdown"
author: "shelleydan"
date: "2024-11-04"
output: html_document
---

```{r setup, include=FALSE}
workDir <- "~/mydata/BIT107-Boar-Markdown/"
projectName <- "Boar_Data_R_Markdown.R"
```

For the analysis of this data set (Boar.csv), there are a few specific packages that need to be installed first. 

```{r Packages, include=FALSE}
#Downloading Packages and Loading Libraries
install.packages("dplyr")
library(dplyr)
```

The first step is to read in the Boar data ("Boar.csv") which includes information based on their size (length) and TB status (tb). The goal of this analysis is to build a generalised linear model (GLM) to predict the possibility of a Boar being infected with TB based on their body length. 

```{r}
boar_data <- read.csv("Boar.csv", header = T, na = "NA", stringsAsFactors = T)

```

Firstly, we want to look at some basic data exploration before we make our model. Here we plot all variable against each other and look at the structure of the data frame. 

```{r}
pairs(boar_data)
glimpse(boar_data)
```



